Biomass and species richness temporal trends drives the assembly and the disassembly of food-web in natural fish assemblages

### 2021-07-01 paper/appendix.Rmd
Add interaction models + surface plot

>>>>

## Interaction between community biomass trends and species richness trends

```{r}
loadd(model_bm_rich_int_mono_stable_trends)
```

### ANOVA

```{r}
model_bm_rich_int_mono_stable_trends %>%
  .[names(.) %in% c("ct_ff", "w_trph_lvl_avg", "piel_bm")] %>%
  map(., car::Anova) %>%
  map(., tidy) %>%
  map2_dfr(., names(.), ~.x %>% mutate(response = .y) %>% select(response,
      everything())) %>%
  kable(., booktabs = TRUE,
  row.names = FALSE,
  caption =
    paste0(
      "ANOVA results with interactions."
      ),
    label = "aov-int"
    ) %>%
kable_styling(latex_options =c("scale_down", "stripped")) %>%
collapse_rows(columns = 1, valign = "top")
#map(model_bm_rich_int_mono_stable_trends, ~try(car::vif(.x)))
```

```{r}
model_bm_rich_int_mono_stable_trends %>%
  .[names(.) %in% c("ct_ff", "w_trph_lvl_avg", "piel_bm")] %>%
  map(., tidy) %>%
  map2_dfr(., names(.), ~.x %>% mutate(response = .y) %>% select(response,
      everything())) %>%
  kable(., booktabs = TRUE,
  row.names = FALSE,
  caption =
    paste0(
      "Regression results with interactions."
      ),
    label = "aov-int"
    ) %>%
kable_styling(latex_options =c("scale_down", "stripped")) %>%
collapse_rows(columns = 1, valign = "top")
```

### Plots

```{r}
pred_int_rich <- map(model_bm_rich_int_mono_stable_trends,
      ~ggpredict(.x,
        terms = c("log_rich_std", "log_bm_std [quart2]")) %>%
        as_tibble() %>%
        mutate(group = as.numeric(as.character(group))) %>%
        rename("log_rich_std" = x, "log_bm_std" = group)
        ) %>%
enframe(name = "response", value = "pred_int")

ti <- pred_bm_rich_mono_stable_trends %>%
  filter(term == "log_rich_std", response %in% c("ct_ff", "w_trph_lvl_avg", "piel_bm")) %>%
  select(response, raw_plot) %>%
  left_join(pred_int_rich) %>%
  mutate(pred_plot_color = pmap(
      list(raw_plot, response, pred_int),
      function(p, resp, pred) {
        p +
          geom_line(data = pred,
            aes(
              y = predicted,
              x = log_rich_std,
              color = as.factor(log_bm_std)
            ), size = 1
          ) +
        scale_color_discrete()
      }
      )
  )
rich_leg <- get_legend(ti$pred_plot_color[[1]])

plot_grid(plotlist = map(ti$pred_plot_color, ~.x + theme(legend.position = "none")), rich_leg)
```

```{r}
test <- pred_int_rich[3, ]$pred_int[[1]] %>%
  select(predicted, log_rich_std, log_bm_std) %>%
  arrange(log_rich_std, log_bm_std)

mat <- reshape2::acast(test, log_rich_std~log_bm_std, value.var = "predicted")
library(plotly)
plot_ly(
  x = ~as.numeric(colnames(mat)),
  y = ~as.numeric(rownames(mat)),
  z = ~mat) %>%
  add_surface()
```

```{r}
pred_int_bm <- map(model_bm_rich_int_mono_stable_trends,
      ~ggpredict(.x,
        terms = c("log_bm_std", "log_rich_std [quart2]")) %>%
        as_tibble() %>%
        mutate(group = as.numeric(as.character(group))) %>%
        rename("log_bm_std" = x, "log_rich_std" = group)
        ) %>%
enframe(name = "response", value = "pred_int")

ti_bm <- pred_bm_rich_mono_stable_trends %>%
  filter(term == "log_bm_std", response %in% c("ct_ff", "w_trph_lvl_avg", "piel_bm")) %>%
  select(response, raw_plot) %>%
  left_join(pred_int_bm) %>%
  mutate(pred_plot_color = pmap(
      list(raw_plot, response, pred_int),
      function(p, resp, pred) {
        p +
          geom_line(data = pred,
            aes(
              y = predicted,
              x = log_bm_std,
              color = as.factor(log_rich_std)
            ), size = 1
          ) +
        scale_color_discrete()
      }
      )
  )

bm_leg <- get_legend(ti_bm$pred_plot_color[[1]])
plot_grid(plotlist = map(ti_bm$pred_plot_color, ~.x + theme(legend.position = "none")), bm_leg)
```

```{r, eval=FALSE}
test <- model_bm_rich_int_mono_stable_trends[["ct_ff"]]
co <- coef(test)
pred <- ggpredict(
  test,
  terms = c("log_bm_std ", "log_rich_std")
  ) %>%
  as_tibble() %>%
  mutate(group = as.numeric(as.character(group))) %>%
  rename("log_bm_std" = x, "log_rich_std" = group)

pred$y <- co[1] +
  co["log_rich_std"] * pred[["log_rich_std"]] +
  co["log_bm_std"] * pred[["log_bm_std"]] +
  co["log_rich_std:log_bm_std"] * pred[["log_rich_std"]] * pred[["log_bm_std"]]

# all.equal(pred$y, pred$predicted)

mat <- reshape2::acast(pred, log_rich_std~log_bm_std, value.var = "y")
library(plotly)
plot_ly(
  x = ~as.numeric(colnames(mat)),
  y = ~as.numeric(rownames(mat)),
  z = ~mat, ) %>%
  add_surface() %>%
  layout(scene = list(
      xaxis = list(title = "species richness"),
      yaxis = list(title = "Community biomass"),
      zaxis = list(title = "Connectance")
      ))
```

```{r, eval=FALSE}
mod4_3d <- model_bm_rich_int_mono_stable_trends[
  names(model_bm_rich_int_mono_stable_trends) %in%
    c("ct_ff", "w_trph_lvl_avg")]

pred_list <- map(mod4_3d,
  function (modl, p) {
    co <- coef(modl)
    p$y <- co[1] +
#      co["log_rich_std"] * p[["log_rich_std"]] +
      co["log_bm_std"] * p[["log_bm_std"]] +
      co["log_rich_std:log_bm_std"] * p[["log_rich_std"]] * p[["log_bm_std"]]
    return(p)

  }, p = pred)
```

```{r,eval=FALSE}
mat <- reshape2::acast(
  pred_list$w_trph_lvl_avg,
  log_rich_std~log_bm_std,
  value.var = "y")
plot_ly(
  x = ~as.numeric(colnames(mat)),
  y = ~as.numeric(rownames(mat)),
  z = ~mat, ) %>%
  add_surface() %>%
  layout(scene = list(
      xaxis = list(title = "Community biomass"),
      yaxis = list(title = "species richness"),
      zaxis = list(title = "Avg trophic level")
      ))
```

```{r,eval=FALSE}
test <- model_bm_rich_int_mono_stable_trends[["piel_bm"]]
car::Anova(test)
co <- coef(test)
pred <- ggpredict(
  test,
  terms = c("log_bm_std ", "log_rich_std")
  ) %>%
  as_tibble() %>%
  mutate(group = as.numeric(as.character(group))) %>%
  rename("log_bm_std" = x, "log_rich_std" = group)

pred$y <- co[1] +
  co["log_rich_std"] * pred[["log_rich_std"]] +
  co["log_bm_std"] * pred[["log_bm_std"]] +
  co["log_rich_std:log_bm_std"] * pred[["log_rich_std"]] * pred[["log_bm_std"]]

# all.equal(pred$y, pred$predicted)

mat <- reshape2::acast(pred, log_rich_std~log_bm_std, value.var = "y")
plot_ly(
  x = ~as.numeric(colnames(mat)),
  y = ~as.numeric(rownames(mat)),
  z = ~mat, ) %>%
  add_surface() %>%
  layout(scene = list(
      xaxis = list(title = "species richness"),
      yaxis = list(title = "Community biomass"),
      zaxis = list(title = "Eveness of biomass")
      ))
```

### 2021-07-01 paper/manuscript.Rmd
Add figures in appendices
Add interaction models + surface plot

fig1_2 <- get_plot_rich_bm(
  predict_plot = pred_bm_rich_mono_stable_trends,
  get_list = TRUE,
  rm_legend = FALSE,
  bm_x = "log_bm_std",
  bm_y = c(get_com_str_var(), "log_rich_std", "piel_nind", "piel_bm"),
  rich_y = c(get_com_str_var(), "log_bm_std", "piel_nind", "piel_bm"),
  rich_x = "log_rich_std"
  )
p_bm <- fig1_2$bm
names(p_bm) <- c("log_rich_std", "ct_ff", "w_trph_lvl_avg",
  "piel_bm", "piel_nind")
#plot_grid(plotlist = p_bm)

@@

```{r}
ti <- list()
for (
  i in c("log_rich_std", "w_trph_lvl_avg", "piel_bm", "piel_nind", "ct_ff")
  ) {
  ti[[i]] <- list(p_bm[[i]], p_sp_bm[[i]])
}
```

```{r bm, fig.height = 12, fig.cap=fig_bm_cap}
# Make the label on two lines
fig1 <- plot_grid(plotlist = c(ti[[1]], ti[[2]], ti[[3]], ti[[4]], ti[[5]]), ncol = 2)
fig1
```

@@

```{r}
trich <- list()
for (i in c("log_bm_std", "w_trph_lvl_avg",  "piel_bm", "piel_nind", "ct_ff")) {
  trich[[i]] <- list(p_rich[[i]], p_sp_rich[[i]])
}
```

```{r rich, fig.height = 12, fig.cap=fig_rich_cap}
# Make the label on two lines
fig2 <- plot_grid(
  plotlist = c(trich[[1]], trich[[2]], trich[[3]], trich[[4]], trich[[5]]),
  ncol = 2)
fig2
```

>>>>

fig1_2 <- get_plot_rich_bm(
  predict_plot = pred_bm_rich_mono_stable_trends,
  get_list = TRUE,
  rm_legend = FALSE,
  bm_x = "log_bm_std",
  bm_y = c("ct_ff", "w_trph_lvl_avg", "piel_bm"), #, "piel_nind"
  rich_y = c("ct_ff", "w_trph_lvl_avg", "log_bm_std", "piel_bm"), #, "piel_nind"
  rich_x = "log_rich_std"
  )
p_bm <- fig1_2$bm
names(p_bm) <- c("ct_ff", "w_trph_lvl_avg", "piel_bm")
plot_grid(plotlist = p_bm)

@@

```{r}
fig_bef_cap <- paste0(
  "Relationship between the temporal trends of community structure
  and the one of species richness. Lines correspond to the predictions of the
  linear models. The lines surrounding each point represent the standard error
  associated to the temporal trends."
)
```
```{r bef, fig.cap=fig_bef_cap}
fig1_2$rich$log_bm_std
```

```{r}
fig_bm_rich_cap <- paste0(
  "Relationship among the temporal trends of community structure
  and the one of species richness and community biomass. The lines
  surrounding each point represent the standard error associated to the temporal
  trends."
)
```
```{r bmr, fig.height = 12, fig.cap=fig_bm_rich_cap}
fig2 <- fig1_2
fig2$rich$log_bm_std <- NULL
plot_grid(
  plot_grid(plotlist = fig2$bm, nrow = 1),
  plot_grid(plotlist = fig2$rich, nrow = 1),
  nrow = 2
)
```

```{r bm, eval=FALSE, fig.height = 12, fig.cap=fig_bm_cap}
ti <- list()
for (
  i in c("log_rich_std", "w_trph_lvl_avg", "piel_bm", "piel_nind", "ct_ff")
  ) {
  ti[[i]] <- list(p_bm[[i]], p_sp_bm[[i]])
}

# Make the label on two lines
fig1 <- plot_grid(plotlist = c(ti[[1]], ti[[2]], ti[[3]], ti[[4]], ti[[5]]), ncol = 2)
fig1
```

@@

```{r rich, eval=FALSE,fig.height = 12, fig.cap=fig_rich_cap}
trich <- list()
for (i in c("log_bm_std", "w_trph_lvl_avg",  "piel_bm", "piel_nind", "ct_ff")) {
  trich[[i]] <- list(p_rich[[i]], p_sp_rich[[i]])
}

# Make the label on two lines
fig2 <- plot_grid(
  plotlist = c(trich[[1]], trich[[2]], trich[[3]], trich[[4]], trich[[5]]),
  ncol = 2)
fig2
```
